---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rgenometracks

<!-- badges: start -->

<!-- badges: end -->

Rgenometrack provides a simple interface for plotting genome tracks using ggplot.

## Installation

You can install the development version of Rgenometracks like so:

``` r
# Install BiocManager if not already installed
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

# Install the package directly from GitHub
BiocManager::install("GKBlomquist/Rgenometracks")
```

## Example

### Single-sample BigWig plot

Plotting a single bigwig track with genes. I recommend using `patchwork` to combine multiple tracks into a single plot. This allows for more advanced options like combining axes and setting individual heights for each track plot.

```{r example}
library(Rgenometracks)
library(ggplot2)
library(patchwork)
library(org.Hs.eg.db)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)

# set unified theme
set_theme_modern()

# set region and reference genome
bw_file = "path/to/bigwig.bw"
region <- "chr2:11446438-11699848"
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene
orgdb <- org.Hs.eg.db

# plot BigWig track
bigwig_track(file = bw_file, region) +

# plot genes in region
genes_track(region, 
            txdb = txdb, orgdb = orgdb, 
            collapse = TRUE, fully_in_view = TRUE) +
  
plot_layout(ncol = 1, axes = "collect_x", heights = c(1, 0.5))
```

### Multi-sample BigWig plot

Currently, automatic multi-sample handling is not supported. However, one can manually plot and compare multiple samples by freezing the y-axis and coloring the samples.

```{r}
# plot BigWig track
sample1_path = "path/to/sample1.bw"
sample2_path = "path/to/sample2.bw"

bigwig_track(file = sample1_path, region, y_max = 1000, color = "red") + 
  labs(tag = "Sample1") + 
  theme(plot.tag = element_text(angle = 270, vjust = 2), plot.tag.position = "right") +
  
bigwig_track(file = sample2_path, region, y_max = 1000, colo = "blue") + 
  labs(tag = "Sample2") +
  theme(plot.tag = element_text(angle = 270, vjust = 2), plot.tag.position = "right") +

# plot genes in region
genes_track(region, 
            txdb = txdb, orgdb = orgdb, 
            collapse = TRUE, fully_in_view = TRUE) +
  
plot_layout(ncol = 1, axes = "collect_x", heights = c(1, 1, 0.5)) 
```

### Additional features

Rgenometracks offers additional features like plotting arcs with `arcs_track` and plotting deep learning model contribution scores using `bigwig_logo_track`.
